---
title: "Manuscript Tables and Figures"
format:
  docx:
    reference-doc: ref.docx
    fig-cap-location: top
execute:
  echo: false
  message: false
  warning: false
---


```{r}
library(CohortCharacteristics)
library(dplyr)
library(ggplot2)
library(IncidencePrevalence)
library(markdown)
library(omopgenerics)
library(OmopSketch)
library(tidyr)
library(visOmopResults)
library(CohortSurvival)
library(flextable)
library(lme4)
library(broom)     
library(glmmTMB)
library(purrr)
library(patchwork)
library(ggh4x)

# whether to run meta analysis
runMetaAnalysis <- FALSE

# preprocess data if it has not been done
fileData <- file.path(getwd(), "data", "shinyData.RData")
if (!file.exists(fileData)) {
  source(file.path(getwd(), "data", "preprocess.R"))
}

# load shiny data
load(fileData)

# source functions
source(file.path(getwd(), "functions.R"))

# Quarto options
knitr::opts_chunk$set(
  out.width  = "95%",  # figures occupy ~95% of document width
  out.height = "auto",
  dpi        = 320,    # ensure figure quality
  fig.width  = 9,      # default aspect ratio (can be overridden per-figure)
  fig.height = 6,
  results    = "asis"  # enable Markdown produced via cat() inside chunks
)

maeCode <- c("miscarriage", "stillbirth", "preterm_labour", "dysfunctional_labour", "antepartum_haemorrhage",  "gestational_diabetes", "preeclampsia", "eclampsia", "hellp", "ectopic_pregnancy", "postpartum_endometritis", "postpartum_haemorrhage", "maternal_death")
maeClean <- c("Miscarriage", "Ectopic pregnancy", "Stillbirth", "Preterm labour", "Dysfunctional labour", "Antepartum haemorrhage",  "Gestational diabetes", "Pre-eclampsia", "Eclampsia", "HELLP", "Postpartum endometritis", "Postpartum haemorrhage", "Maternal death")
aesiCode <- c("deep_vein_thrombosis", "pulmonary_embolism", "bells_palsy", "immune_thrombocytopenia", "anaphylaxis", "myocarditis_or_pericarditis", "ischaemic_stroke", "haemorrhagic_stroke", "tts",  "guillain_barre_syndrome",  "disseminated_intravascular_coagulation", "transverse_myelitis", "narcolepsy", "myocardial_infarction", "encephalitis")
aesiClean <- c('Deep vein thrombosis', 'Pulmonary embolism', 'Bell’s palsy', 'Immune thrombocytopenia', 'Anaphylaxis', 'Myocarditis or pericarditis', 'Ischaemic stroke', 'Haemorrhagic stroke', 'Thrombosis with thrombocytopenia syndrome', 'Guillain–Barré syndrome', 'Disseminated intravascular coagulation', 'Transverse myelitis', 'Narcolepsy', 'Myocardial infarction', 'Encephalitis')
excludeCPRD <- c("Miscarriage", "Stillbirth")
dbOrder <- c("NLHR@UiO", "SCIFI-PEARL", "SIDIAP", "CPRD GOLD")

setGlobalTableOptions(type = "flextable")
```

:::{custom-style="Caption"}
Table 1. Characteristics of included pregnancies, stratified by database. 

:::

```{r}
# prepare results ----
data$summarise_characteristics |>
  dplyr::filter(group_level == "pregnancy_denominator", strata_name == "overall") |>
  dplyr::filter(
    !variable_name %in% c("Cohort start date", "Cohort end date", "Age", "Sex", "Prior observation", "Future observation")
  ) |>
  dplyr::mutate(
    estimate_value = if_else(variable_name == "Previous pregnancies", as.character(as.numeric(.data$estimate_value) - 1), .data$estimate_value),
    cdm_name = factor(cdm_name, levels = dbOrder),
    variable_level = dplyr::if_else(variable_name == "Previous pregnancies", "-", variable_level),
    variable_name = factor(
      variable_name,
      levels = c(
        "Number records", 
        "Maternal age", 
        "Maternal age group",
        "Days in cohort", 
        "Previous pregnancies", 
        "Covariates in the past 5 years",
        "History of comorbidities", 
        "Medications in the past year"
      ),
      labels = c(
        "Number pregnancies", 
        "Maternal age", 
        "Maternal age group",
        "Pregnancy length", 
        "Previous pregnancies",
        "Covariates (previous 5 years)",
        "Comorbidities (any-time before)",
        "Medications (previous year)"
      )
    ),
    variable_level = factor(
      variable_level,
      levels = c(
        "12 to 17", "18 to 34", "35 to 55", "-", 
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse dependence", 
        
        "Asthma", "Diabetes", "Thyroid disorder", 
        "Essential hypertension", 
        "Systemic lupus erythematosus", "Hiv", 
        
        "Antidepressants", "Antiinflammatory antirheumatic", "Nsaids", 
        "Opioids", "Treatment acid related disorder", "Antiepileptics", 
        "Diabetes treatments"
      ),
      labels = c(
        "12 to 17", "18 to 34", "35 to 55", "-", 
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse dependence", 
        
        "Asthma", "Diabetes", "Thyroid disorder", 
        "Essential hypertension", 
        "SLE", "HIV", 
        
        "Antidepressants", "Antiinflammatory antirheumatic", "NSAIDs", 
        "Opioids", "Acid-related disorder treatments", "Antiepileptics", 
        "Diabetes treatments"
      )
    )
  ) |>
  dplyr::filter(!is.na(variable_name)) |>
  dplyr::arrange(cdm_name, variable_name, variable_level) |>
  visOmopTable(
    estimateName = c(
      "N (%)" = "<count> (<percentage>%)",
      "N" = "<count>",
      "Median [Q25 to Q75]" = "<median> [<q25> to <q75>]"
    ),
    rename = c("Database" = "cdm_name"),
    header = "cdm_name",
    hide = c("cohort_name", strataColumns(data$summarise_characteristics)),
    .options = list(keepNotFormatted = FALSE, groupAsColumn = TRUE),
    groupColumn = "variable_name"
  ) |>
  set_table_properties(width = 1, layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header") |>
  width(j = 1, width = 2.3, unit = "cm") |>
  width(j = 1:3, width = 2.66, unit = "cm") |>
  width(j = 1:3, width = 2.3, unit = "cm")
```

:::{custom-style="FooterNuria"}
SLE = Systemic Lupus Erythematosus; HIV = Human Immunodeficiency Virus; NSAIDs = Nonsteroidal Anti-Inflammatory Drugs
:::





:::{custom-style="Caption"}
Table 2. Pooled Incidence Rates (per 100,000 person-years) and 95% Prediction Intervals for adverse events across four databases.

:::

```{r}
# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("overall", "gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Maternal Adverse Events", "Adverse Events of Special Interest")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count", "incidence_100000_pys", "incidence_100000_pys_95CI_lower", "incidence_100000_pys_95CI_upper", "outcome_in_period_count", "outcome_in_period_percentage"
  ))

# pool results ----
# --> model event counts using a Poisson distribution
# --> account for different amounts of person-time in each database
# --> random-effect for between-database heterogeneity. random intercept for database (1 | cdm_name)
# --> consider databases with zero events
if (runMetaAnalysis) {
  data$meta_incidence <- tidyIncidence |>
    filter(!is.na(outcome_count), !is.na(person_years)) |>
    group_by(
      outcome_cohort_name,
      gestational_trimester,
      maternal_age_group,
      pregnancy_start_period,
      outcome_group
    ) |>
    nest() |>
    mutate(
      meta = map(data, metaIR)
    ) |>
    unnest(meta) |>
    ungroup() |>
    select(!data)
  save(data, choices, selected, values, file = file.path(getwd(), "data", "shinyData.RData"))
} 

# display results ----
data$meta_incidence |>
  dplyr::filter(
    gestational_trimester == "overall",
    maternal_age_group == "overall",
    pregnancy_start_period == "overall"
  ) |>
  select(!c("gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  pivot_longer(
    cols = c("pooled_incidence_100000_pys", "predicted_interval_95CI_lower", "predicted_interval_95CI_upper", "tau2", "denominator_count", "outcome_count", "outcome_percentage", "number_of_databases", "person_years"),
    values_to = "estimate_value",
    names_to = "estimate_name"
  ) |>
  mutate(
    estimate_type = case_when(
      grepl("count", estimate_name) | estimate_name == "number_of_databases" ~ "integer",
      grepl("percentage", estimate_name) | estimate_name == "tau2" ~ "percentage",
      .default = "numeric"
    ),
    outcome = factor(.data$outcome_cohort_name, levels = c(aesiClean, maeClean)),
    estimate_value = as.character(estimate_value)
  ) |>
  filter(!is.na(outcome)) |>
  arrange(outcome) |>
  select(!"outcome_cohort_name") |>
  visTable(
    estimateName = c(
      "Databases (N)" = "<number_of_databases>",
      "Pregnancies (N)" = "<denominator_count>",
      "Outcomes (N (%))" = "<outcome_count> (<outcome_percentage>%)",
      "Person-Years" = "<person_years>",
      "IR (95% PI)" = "<pooled_incidence_100000_pys> (<predicted_interval_95CI_lower> to <predicted_interval_95CI_upper>)",
      "𝜏²" = "<tau2>"
    ),
    hide = "estimate_type",
    header = "estimate_name",
    groupColumn = "outcome_group",
    .options = list(decimals = c(integer = 0, percentage = 3, numeric = 2))
  ) |>
  set_table_properties(width = 1, layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header")
```

:::{custom-style="FooterNuria"}
Pooled incidence rates were estimated per 100,000 person-years using Poisson generalized linear mixed models with a random intercept for database; 95% prediction intervals reflect between-database heterogeneity. Source-specific estimates are shown in Supplementary Table Sx. Databases with event counts <5 were clouded as per data-protection rules and were not included in pooled estimates. 
IR = Incidence Rate; PI = Prediction Interval; 𝜏² = estimated in between-database variance
:::


:::{custom-style="Caption"}
Figure 1. Incidence rates per 100,000 person-years for the 6-most frequent Adverse Events of Special Interest among pregnant women, stratified by gestational trimester and database.
:::

```{r,  fig.height = 9}
# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester", "maternal_age_group")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Adverse Events of Special Interest")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count"
  )) |>
  filter(!outcome_cohort_name %in% c("Thrombosis with thrombocytopenia syndrome", "Narcolepsy", "Disseminated intravascular coagulation", "Encephalitis", "Guillain–Barré syndrome", "Myocardial infarction", "Transverse myelitis", "Ischaemic stroke", "Haemorrhagic stroke")) |>
  mutate(
    outcome_cohort_name = factor(.data$outcome_cohort_name, levels = aesiClean),
    cdm_name = factor(cdm_name, dbOrder)
  ) |>
  arrange(cdm_name, outcome_cohort_name)

pTrimester <- pIncidence(tidyIncidence |> filter(maternal_age_group == "overall"), "gestational_trimester", "free_y") +
   ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(limits = c(0,170), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(limits = c(0,250), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(limits = c(0,170), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(limits = c(0,150), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(limits = c(0,50), oob = scales::rescale_none),
       outcome_cohort_name == "Myocarditis or pericarditis" ~ scale_y_continuous(limits = c(0,30), oob = scales::rescale_none)
     )
   ) +
  ggtitle("A) Incidence Rates by Gestational Trimester") +
  theme(title = element_text(face = "bold", size = 13))
pAge <- pIncidence(tidyIncidence |> filter(gestational_trimester == "overall"), "maternal_age_group", "free_y") +
  # scale_y_continuous(limits = c(0,150)) +
  theme(legend.position = "none") +
     ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(limits = c(0,150), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(limits = c(0,250), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(limits = c(0,100), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(limits = c(0,100), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(limits = c(0,40), oob = scales::rescale_none),
       outcome_cohort_name == "Myocarditis or pericarditis" ~ scale_y_continuous(limits = c(0,25), oob = scales::rescale_none)
     )
   ) +
  ggtitle("B) Incidence Rates by Age") +
  theme(title = element_text(face = "bold", size = 13))

pTrimester / pAge + 
  plot_layout(heights = c(2, 1.9)) 
```

```{r,  fig.height = 9}
# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester", "maternal_age_group")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Adverse Events of Special Interest")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count"
  )) |>
  filter(!outcome_cohort_name %in% c("Thrombosis with thrombocytopenia syndrome", "Narcolepsy", "Disseminated intravascular coagulation", "Encephalitis", "Guillain–Barré syndrome", "Myocardial infarction", "Transverse myelitis", "Ischaemic stroke", "Haemorrhagic stroke")) |>
  mutate(
    outcome_cohort_name = factor(.data$outcome_cohort_name, levels = aesiClean),
    cdm_name = factor(cdm_name, dbOrder)
  ) |>
  arrange(cdm_name, outcome_cohort_name)

pTrimester <- pIncidence(tidyIncidence |> filter(maternal_age_group == "overall"), "gestational_trimester", "free_y", FALSE) +
   ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(limits = c(0,170), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(limits = c(0,250), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(limits = c(0,170), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(limits = c(0,150), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(limits = c(0,50), oob = scales::rescale_none),
       outcome_cohort_name == "Myocarditis or pericarditis" ~ scale_y_continuous(limits = c(0,30), oob = scales::rescale_none)
     )
   ) +
  ggtitle("A) Incidence Rates by Gestational Trimester") +
  theme(title = element_text(face = "bold", size = 13))
pAge <- pIncidence(tidyIncidence |> filter(gestational_trimester == "overall"), "maternal_age_group", "free_y", FALSE) +
  # scale_y_continuous(limits = c(0,150)) +
  theme(legend.position = "none") +
     ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(limits = c(0,150), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(limits = c(0,250), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(limits = c(0,100), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(limits = c(0,100), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(limits = c(0,40), oob = scales::rescale_none),
       outcome_cohort_name == "Myocarditis or pericarditis" ~ scale_y_continuous(limits = c(0,25), oob = scales::rescale_none)
     )
   ) +
  ggtitle("B) Incidence Rates by Age") +
  theme(title = element_text(face = "bold", size = 13))

pTrimester / pAge + 
  plot_layout(heights = c(2, 1.9)) 
```

:::{custom-style="Caption"}
Figure 2. Cumulative curves for Maternal Adverse Events across databases.
:::

```{r, fig.width=10}
survivalTidy <- data$survival |>
  dplyr::filter(strata_name %in% c("overall", "maternal_age_group")) |>
  asSurvivalResult() |>
  dplyr::mutate(
    outcome = factor(.data$outcome, levels = maeCode,  labels = maeClean),
    cdm_name = factor(cdm_name, dbOrder)
  ) |>
  dplyr::filter(!is.na(outcome)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & outcome %in% excludeCPRD)) |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "competing_outcome"
  )) |>
  arrange(cdm_name, outcome)

colors <- c("#C94A5A", "#4A6FE3", "#4FAE6A", "#E08A3C")
survivalTidy |>
  filter(maternal_age_group == "overall") |>
  pSurvival() +
  geom_vline(data = filter(survivalTidy, !grepl("Postpartum", outcome) & maternal_age_group == "overall"), aes(xintercept = 90), colour = "#495057", linetype = "dashed") +
  geom_vline(data = filter(survivalTidy, !grepl("Postpartum", outcome) & maternal_age_group == "overall"), aes(xintercept = 180), colour = "#495057", linetype = "dashed") +
  facet_wrap(vars(outcome), nrow = 3, ncol = 5, scales = "free", labeller = label_wrap_gen(10)) +
  ggh4x::facetted_pos_scales(
    y  = list(
      outcome == "Ectopic pregnancy" ~ scale_y_continuous(limits = c(0,0.05), oob = scales::rescale_none),
      outcome == "Antepartum haemorrhage" ~ scale_y_continuous(limits = c(0,0.08), oob = scales::rescale_none),
      outcome == "Gestational diabetes" ~ scale_y_continuous(limits = c(0,0.1), oob = scales::rescale_none),
      outcome == "Pre-eclampsia" ~ scale_y_continuous(labels = scales::label_comma(), oob = scales::rescale_none),
      outcome == "Eclampsia"  ~ scale_y_continuous(limits = c(0,0.005), oob = scales::rescale_none)
    )
  )
```

:::{custom-style="Caption"}
Figure 3. Cumulative incidence curves for Maternal Adverse Events across databases, stratified by age.
:::

```{r, fig.height=14}
colors <- c("#C94A5A", "#4A6FE3", "#4FAE6A", "#E08A3C")
survivalTidyAge <- survivalTidy |>
  filter(maternal_age_group != "overall") |>
  mutate(maternal_age_group = as.character(maternal_age_group))
survivalTidyAge |>
  pSurvival() +
  geom_vline(data = filter(survivalTidyAge, !grepl("Postpartum", outcome)), aes(xintercept = 90), colour = "#495057", linetype = "dashed") +
  geom_vline(data = filter(survivalTidyAge, !grepl("Postpartum", outcome)), aes(xintercept = 180), colour = "#495057", linetype = "dashed") +
  facet_grid(rows = vars(outcome), cols = vars(maternal_age_group), scales = "free", labeller = label_wrap_gen(10)) +
  ggh4x::facetted_pos_scales(
    # x  = list(
    #   grepl("Postpartum", outcome) ~ scale_x_continuous(limits = c(0,84)),
    #   !grepl("Postpartum", outcome) ~ scale_x_continuous(limits = c(0,308))
    # ),
    y  = list(
      outcome == "Ectopic pregnancy" ~ scale_y_continuous(limits = c(0,0.03), oob = scales::rescale_none),
      outcome == "Antepartum haemorrhage" ~ scale_y_continuous(limits = c(0,0.05), oob = scales::rescale_none),
      outcome == "Gestational diabetes" ~ scale_y_continuous(limits = c(0,0.08), oob = scales::rescale_none),
      outcome == "Pre-eclampsia" ~ scale_y_continuous(limits = c(0,0.001), labels = scales::label_comma(), oob = scales::rescale_none),
      outcome == "Eclampsia" ~ scale_y_continuous(limits = c(0,0.003), oob = scales::rescale_none),
      outcome == "Postpartum endometritis" ~ scale_y_continuous(limits = c(0,0.006), oob = scales::rescale_none),
      outcome == "Postpartum haemorrhage" ~ scale_y_continuous(limits = c(0,0.02), oob = scales::rescale_none)
    )
  )
```

:::{custom-style="Caption"}
Figure 3. Incidence rates for Maternal Adverse Events across databases, stratified by age.
:::

```{r, fig.height=9}
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester", "maternal_age_group")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Maternal Adverse Events")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
    dplyr::filter(group_level != "Maternal death") |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count"
  )) |>
  mutate(
    outcome_cohort_name = factor(.data$outcome_cohort_name, levels = maeClean),
    cdm_name = factor(cdm_name, dbOrder)
  ) |>
  arrange(cdm_name, outcome_cohort_name)

pAge <- pIncidence(tidyIncidence |> filter(gestational_trimester == "overall"), "maternal_age_group", "free_y", FALSE) +
  facet_wrap(vars(outcome_cohort_name), scales = "free_y") +
   ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Ectopic pregnancy" ~ scale_y_continuous(limits = c(0,3600), oob = scales::rescale_none),
       outcome_cohort_name == "Stillbirth" ~ scale_y_continuous(limits = c(0,36000), oob = scales::rescale_none),
       outcome_cohort_name == "Pre-eclampsia" ~ scale_y_continuous(limits = c(0, 50), oob = scales::rescale_none),
       outcome_cohort_name == "Eclampsia" ~ scale_y_continuous(limits = c(0,200), oob = scales::rescale_none),
       outcome_cohort_name == "HELLP" ~ scale_y_continuous(limits = c(0,3000), oob = scales::rescale_none),
       outcome_cohort_name == "Postpartum endometritis" ~ scale_y_continuous(limits = c(0,2000), oob = scales::rescale_none),
       outcome_cohort_name == "Postpartum haemorrhage" ~ scale_y_continuous(limits = c(0,7500), oob = scales::rescale_none)
     )
   ) 
pAge
```