---
title: "Background rates of maternal adverse events"
format: docx
execute:
  echo: false
  message: false
  warning: false
---


```{r}
library(CohortCharacteristics)
library(dplyr)
library(ggplot2)
library(IncidencePrevalence)
library(markdown)
library(omopgenerics)
library(OmopSketch)
library(tidyr)
library(visOmopResults)
library(CohortSurvival)
library(flextable)

# preprocess data if it has not been done
fileData <- file.path(getwd(), "data", "shinyData.RData")
if (!file.exists(fileData)) {
  source(file.path(getwd(), "data", "preprocess.R"))
}

# load shiny data
load(fileData)

# source functions
source(file.path(getwd(), "functions.R"))

# Quarto options
knitr::opts_chunk$set(
  out.width  = "95%",  # figures occupy ~95% of document width
  out.height = "auto",
  dpi        = 320,    # ensure figure quality
  fig.width  = 9,      # default aspect ratio (can be overridden per-figure)
  fig.height = 6,
  results    = "asis"  # enable Markdown produced via cat() inside chunks
)

outcomeCode <- c("miscarriage", "stillbirth", "preterm_labour", "dysfunctional_labour", "antepartum_haemorrhage",  "gestational_diabetes", "preeclampsia", "eclampsia", "hellp", "ectopic_pregnancy", "postpartum_endometritis", "postpartum_haemorrhage", "maternal_death")
outcomeClean <- c("Miscarriage", "Ectopic pregnancy", "Stillbirth", "Preterm labour", "Dysfunctional labour", "Antepartum haemorrhage",  "Gestational diabetes", "Pre-eclampsia", "Eclampsia", "HELLP", "Postpartum endometritis", "Postpartum haemorrhage", "Maternal death")
excludeCPRD <- c("Miscarriage", "Stillbirth")
dbOrder <- c("NLHR@UiO", "SCIFI-PEARL", "SIDIAP", "CPRD GOLD")

setGlobalTableOptions(type = "flextable")
```

# Maternal Adverse Events

## Overall incidence by data source

Table of overall incidence rates for Maternal Adverse Events across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r}
# Table 
table <- data$incidence |>
  dplyr::filter(strata_name == "overall") |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD))

table <- dplyr::bind_rows(
  table, 
  table |>
    omopgenerics::pivotEstimates() |>
    dplyr::mutate(estimate_value = if_else(!is.na(outcome_count), as.character(outcome_count/denominator_count * 100), NA_character_)) |>
    dplyr::mutate(
      estimate_name = "outcome_percentage",
      estimate_type = "percentage"
    )  |>
    dplyr::select(omopgenerics::resultColumns())
)
table |>
  dplyr::filter(!estimate_name %in% c("person_days_count", "outcome_in_period_count")) |>
  dplyr::mutate(group_name = "outcome") |>
  newSummarisedResult(settings = settings(data$incidence) |> mutate(group = "outcome")) |>
  visOmopResults::visOmopTable(
    estimateName = c(
      "Pregnancies" = "<denominator_count>",
      "Outcomes" = "<outcome_count> (<outcome_percentage> %)",
      "Outcomes in period" = "<outcome_in_period_count> (<outcome_in_period_percentage>%)",
      "Person-Days" = "<person_days_count>",
      "Person-Years" = "<person_years>",
      "Incidence" = c("<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)")
    ),
    header = "cdm_name",
    groupColumn = c("outcome"),
    hide = c("outcome_group", "gestational_trimester", "maternal_age_group", "pregnancy_start_period", "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level"),
    columnOrder = c(
      "cdm_name", "outcome_group", "outcome", "gestational_trimester", "maternal_age_group", "pregnancy_start_period",  
      "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level", "estimate_name"
    ),
    factor = list(
      "cdm_name" = dbOrder,
      "outcome_group" = c("Maternal Adverse Events", "AESI Sensitivity (180 wash-out)"),
      "outcome" = outcomeClean,
      "maternal_age_group" = c("overall", "12 to 17", "18 to 34", "35 to 55"),
      "pregnancy_start_period" = c("overall", "Pre COVID-19", "COVID-19 main outbreak", "Post COVID-19 main outbreak"),
      "socioeconomic_status" = c("overall", paste0("Q", 1:5)),
      "ethnicity" = c("overall", "White", "Black", "Asian", "Missing"),
      "gestational_trimester" = c("overall", "Trimester 1", "Trimester 2", "Trimester 3", "Postpartum")
    ),
    rename = c("Database" = "cdm_name")
  ) |>
  set_table_properties(width = 1, layout = "autofit")
```

Figure of cumulative incidence for Maternal Adverse Events across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r}
# Figure 
table <- data$survival |>
  omopgenerics::filterSettings(outcome %in% outcomeCode) |>
  omopgenerics::filterSettings(result_type == "survival_probability") |>
  dplyr::filter(strata_name == "overall") |>
  tidy() |>
  dplyr::mutate(
    outcome = factor(
      .data$outcome, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    cdm_name = factor(cdm_name, levels = dbOrder, labels = dbOrder),
    time = as.numeric(time),
    estimate = 1 - estimate,
    estimate_95CI_lower = 1 - estimate_95CI_lower,
    estimate_95CI_upper = 1 - estimate_95CI_upper
  ) |>
  dplyr::filter(!is.na(outcome)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & outcome %in% excludeCPRD)) 
colors <- c(
  "#C94A5A",  # Muted red
  "#4A6FE3",  # Professional blue
  "#4FAE6A",  # Academic green
  "#E08A3C"   # Muted orange
)
table |>
  ggplot(
    aes(
      x = time,
      y = estimate,
      ymin = estimate_95CI_upper,
      ymax = estimate_95CI_lower,
      color = cdm_name,
      fill  = cdm_name,
      group = cdm_name
    )
  ) +
  geom_ribbon(
    alpha = 0.15,
    color = NA,
    show.legend = FALSE
  ) +
  # geom_errorbar(
  #   width = 0.15,
  #   linewidth = 0.5
  # ) +
  geom_line() +
  facet_wrap(vars(outcome), scales = "free_y") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  guides(
    color = guide_legend(title = "Database"),
    fill  = guide_legend(title = "Database")
  ) +
  theme_bw() +
  theme(
    # strip.background = element_rect(fill = "white", color = "black", linewidth = 0.5),
    strip.text = element_text(face = "bold", size = 10, colour = "black"),
    # axis.title.x = element_text(margin = margin(t = 6)),
    # axis.title.y = element_text(margin = margin(r = 6)),
    legend.position = "top",
    legend.title = element_text(face = "bold")
  ) +
  xlab("Days") +
  ylab("Cumulative Incidence")
```


## Incidence by data source and trimester

Figure of incidence rates for Maternal Adverse Events by gestational trimester, and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r}
# Figure 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  tidy() |>
  dplyr::mutate(
    outcome_cohort_name = factor(
      .data$outcome_cohort_name, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    cdm_name = factor(cdm_name, levels = dbOrder, labels = dbOrder),
    gestational_trimester = factor(gestational_trimester, levels = c(paste0("Trimester ", 1:3), "Postpartum")) 
  ) |>
  dplyr::filter(!is.na(outcome_cohort_name)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & outcome_cohort_name %in% excludeCPRD))
colors <- c(
  "#C94A5A",  # Muted red
  "#4A6FE3",  # Professional blue
  "#4FAE6A",  # Academic green
  "#E08A3C"   # Muted orange
)

table |>
  # filter(!grepl("Postpartum", gestational_trimester)) |>
  ggplot(
    aes(
      x = gestational_trimester,
      y = incidence_100000_pys,
      ymin = incidence_100000_pys_95CI_lower,
      ymax = incidence_100000_pys_95CI_upper,
      color = cdm_name,
      fill  = cdm_name,
      group = cdm_name
    )
  ) +
  geom_ribbon(
    alpha = 0.15,
    color = NA,
    show.legend = FALSE
  ) +
  geom_errorbar(
    width = 0.15,
    linewidth = 0.5
  ) +
  geom_point(
    size = 1.8
  ) +
  geom_line(linewidth = 0.25) +
  facet_wrap(vars(outcome_cohort_name), scales = "free_y") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  guides(
    color = guide_legend(title = "Database"),
    fill  = guide_legend(title = "Database")
  ) +
  theme_bw() +
  theme(
    # strip.background = element_rect(fill = "white", color = "black", linewidth = 0.5),
    strip.text = element_text(face = "bold", size = 10, colour = "black"),
    # axis.title.x = element_text(margin = margin(t = 6)),
    # axis.title.y = element_text(margin = margin(r = 6)),
    legend.position = "top",
    legend.title = element_text(face = "bold")
  ) +
  xlab("") +
  ylab("Incidence per 100,000 person-years")
```

Table of incidence rates for Maternal Adverse Events by gestational trimester, and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r, fig.width=8.5, fig.height=6}
# Table 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD))
table <- dplyr::bind_rows(
  table, 
  table |>
    omopgenerics::pivotEstimates() |>
    dplyr::mutate(estimate_value = if_else(!is.na(outcome_count), as.character(outcome_count/denominator_count * 100), NA_character_)) |>
    dplyr::mutate(
      estimate_name = "outcome_percentage",
      estimate_type = "percentage"
    )  |>
    dplyr::select(omopgenerics::resultColumns())
)
table |>
  dplyr::filter(!estimate_name %in% c("person_days_count", "outcome_in_period_count")) |>
  dplyr::mutate(group_name = "outcome") |>
  newSummarisedResult(settings = settings(data$incidence) |> mutate(group = "outcome")) |>
  visOmopResults::visOmopTable(
    estimateName = c(
      "Pregnancies" = "<denominator_count>",
      "Outcomes" = "<outcome_count> (<outcome_percentage> %)",
      "Outcomes in period" = "<outcome_in_period_count> (<outcome_in_period_percentage>%)",
      "Person-Days" = "<person_days_count>",
      "Person-Years" = "<person_years>",
      "Incidence" = c("<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)")
    ),
    header = c("estimate_name"),
    groupColumn = c("outcome"),
    hide = c("outcome_group", "maternal_age_group", "pregnancy_start_period", "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level"),
    columnOrder = c(
      "cdm_name", "outcome_group", "outcome", "gestational_trimester", "maternal_age_group", "pregnancy_start_period",  
      "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level", "estimate_name"
    ),
    factor = list(
      "cdm_name" = dbOrder,
      "gestational_trimester" = c("overall", "Trimester 1", "Trimester 2", "Trimester 3", "Postpartum"),
      "outcome_group" = c("Maternal Adverse Events", "AESI Sensitivity (180 wash-out)"),
      "outcome" = outcomeClean,
      "maternal_age_group" = c("overall", "12 to 17", "18 to 34", "35 to 55"),
      "pregnancy_start_period" = c("overall", "Pre COVID-19", "COVID-19 main outbreak", "Post COVID-19 main outbreak"),
      "socioeconomic_status" = c("overall", paste0("Q", 1:5)),
      "ethnicity" = c("overall", "White", "Black", "Asian", "Missing")
    ),
    rename = c("Database" = "cdm_name")
  ) |>
  set_table_properties(width = 1, layout = "autofit")
```

## Incidence by data source and age group

Figure of incidence rates for Maternal Adverse Events by maternal age, and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r}
# Figure 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("maternal_age_group")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  tidy() |>
  dplyr::mutate(
    outcome_cohort_name = factor(
      .data$outcome_cohort_name, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    cdm_name = factor(cdm_name, levels = dbOrder, labels = dbOrder)
  ) |>
  dplyr::filter(!is.na(outcome_cohort_name)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & outcome_cohort_name %in% excludeCPRD))

colors <- c(
  "#C94A5A",  # Muted red
  "#4A6FE3",  # Professional blue
  "#4FAE6A",  # Academic green
  "#E08A3C"   # Muted orange
)

table |>
  ggplot(
    aes(
      x = maternal_age_group,
      y = incidence_100000_pys,
      ymin = incidence_100000_pys_95CI_lower,
      ymax = incidence_100000_pys_95CI_upper,
      color = cdm_name,
      fill  = cdm_name,
      group = cdm_name
    )
  ) +
  geom_ribbon(
    alpha = 0.15,
    color = NA,
    show.legend = FALSE
  ) +
  geom_errorbar(
    width = 0.15,
    linewidth = 0.5
  ) +
  geom_point(
    size = 1.8
  ) +
  facet_wrap(vars(outcome_cohort_name), scales = "free_y") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  guides(
    color = guide_legend(title = "Database"),
    fill  = guide_legend(title = "Database")
  ) +
  theme_bw() +
  theme(
    # strip.background = element_rect(fill = "white", color = "black", linewidth = 0.5),
    strip.text = element_text(face = "bold", size = 10, colour = "black"),
    # axis.title.x = element_text(margin = margin(t = 6)),
    # axis.title.y = element_text(margin = margin(r = 6)),
    legend.position = "top",
    legend.title = element_text(face = "bold")
  ) +
  xlab("") +
  ylab("Incidence per 100,000 person-years") 
  # scale_y_continuous(limits = c(0, 500), oob = scales::rescale_none)
```
Table of incidence rates for Maternal Adverse Events by maternal age and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r, fig.width=8.5, fig.height=6}
# Table 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("maternal_age_group")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD))
table <- dplyr::bind_rows(
  table, 
  table |>
    omopgenerics::pivotEstimates() |>
    dplyr::mutate(estimate_value = if_else(!is.na(outcome_count), as.character(outcome_count/denominator_count * 100), NA_character_)) |>
    dplyr::mutate(
      estimate_name = "outcome_percentage",
      estimate_type = "percentage"
    )  |>
    dplyr::select(omopgenerics::resultColumns())
)
table |>
  dplyr::filter(!estimate_name %in% c("person_days_count", "outcome_in_period_count", "outcome_in_period_percentage")) |>
  dplyr::mutate(group_name = "outcome") |>
  newSummarisedResult(settings = settings(data$incidence) |> mutate(group = "outcome")) |>
  visOmopResults::visOmopTable(
    estimateName = c(
      "Pregnancies" = "<denominator_count>",
      "Outcomes" = "<outcome_count> (<outcome_percentage> %)",
      "Outcomes in period" = "<outcome_in_period_count> (<outcome_in_period_percentage>%)",
      "Person-Days" = "<person_days_count>",
      "Person-Years" = "<person_years>",
      "Incidence" = c("<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)")
    ),
    header = c("estimate_name"),
    groupColumn = c("outcome"),
    hide = c("outcome_group", "gestational_trimester", "pregnancy_start_period", "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level"),
    columnOrder = c(
      "cdm_name", "outcome_group", "outcome", "gestational_trimester", "maternal_age_group", "pregnancy_start_period",  
      "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level", "estimate_name"
    ),
    factor = list(
      "cdm_name" = dbOrder,
      "gestational_trimester" = c("overall", "Trimester 1", "Trimester 2", "Trimester 3", "Postpartum"),
      "outcome_group" = c("Maternal Adverse Events", "AESI Sensitivity (180 wash-out)"),
      "outcome" = outcomeClean,
      "maternal_age_group" = c("overall", "12 to 17", "18 to 34", "35 to 55"),
      "pregnancy_start_period" = c("overall", "2018-2019", "2020-2021", "≥2021"),
      "socioeconomic_status" = c("overall", paste0("Q", 1:5)),
      "ethnicity" = c("overall", "White", "Black", "Asian", "Missing")
    ),
    rename = c("Database" = "cdm_name")
  ) |>
  set_table_properties(width = 1, layout = "autofit")
```


## Incidence by data source and calendar time

Figure of incidence rates for Maternal Adverse Events by calendar time, and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r}
# Figure 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  tidy() |>
  dplyr::mutate(
    outcome_cohort_name = factor(
      .data$outcome_cohort_name, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    cdm_name = factor(cdm_name, levels = dbOrder, labels = dbOrder),
    pregnancy_start_period = factor(pregnancy_start_period, levels = c("Pre COVID-19", "COVID-19 main outbreak", "Post COVID-19 main outbreak"), labels = c("2018-2019", "2020-2021", "≥2021"))
  ) |>
  dplyr::filter(!is.na(outcome_cohort_name)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & outcome_cohort_name %in% excludeCPRD))

colors <- c(
  "#C94A5A",  # Muted red
  "#4A6FE3",  # Professional blue
  "#4FAE6A",  # Academic green
  "#E08A3C"   # Muted orange
)

table |>
  ggplot(
    aes(
      x = pregnancy_start_period,
      y = incidence_100000_pys,
      ymin = incidence_100000_pys_95CI_lower,
      ymax = incidence_100000_pys_95CI_upper,
      color = cdm_name,
      fill  = cdm_name,
      group = cdm_name
    )
  ) +
  geom_ribbon(
    alpha = 0.15,
    color = NA,
    show.legend = FALSE
  ) +
  geom_errorbar(
    width = 0.15,
    linewidth = 0.5
  ) +
  geom_point(
    size = 1.8
  ) +
  geom_line(linewidth = 0.25) +
  facet_wrap(vars(outcome_cohort_name), scale = "free_y") +
  scale_color_manual(values = colors) +
  scale_fill_manual(values = colors) +
  guides(
    color = guide_legend(title = "Database"),
    fill  = guide_legend(title = "Database")
  ) +
  theme_bw() +
  theme(
    # strip.background = element_rect(fill = "white", color = "black", linewidth = 0.5),
    strip.text = element_text(face = "bold", size = 10, colour = "black"),
    # axis.title.x = element_text(margin = margin(t = 6)),
    # axis.title.y = element_text(margin = margin(r = 6)),
    legend.position = "top",
    legend.title = element_text(face = "bold")
  ) +
  xlab("") +
  ylab("Incidence per 100,000 person-years")
```

Table of incidence rates for Maternal Adverse Events by calendar time, and across four databases: SCIFI-PEARL, NLHR@UiO, SIDIAP, and CPRD GOLD.
```{r, fig.width=8.5, fig.height=6}
# Table 
table <- data$incidence |>
  dplyr::filter(strata_name %in% c("pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group == "Maternal Adverse Events") |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = outcomeCode, 
      labels = outcomeClean
    ),
    group_level = as.character(group_level),
     strata_level = factor(strata_level, levels = c("Pre COVID-19", "COVID-19 main outbreak", "Post COVID-19 main outbreak"), labels = c("2018-2019", "2020-2021", "≥2021")),
    strata_level = as.character(strata_level),
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD))
table <- dplyr::bind_rows(
  table, 
  table |>
    omopgenerics::pivotEstimates() |>
    dplyr::mutate(estimate_value = if_else(!is.na(outcome_count), as.character(outcome_count/denominator_count * 100), NA_character_)) |>
    dplyr::mutate(
      estimate_name = "outcome_percentage",
      estimate_type = "percentage"
    )  |>
    dplyr::select(omopgenerics::resultColumns())
)
table |>
  dplyr::filter(!estimate_name %in% c("person_days_count", "outcome_in_period_count", "outcome_in_period_percentage")) |>
  dplyr::mutate(group_name = "outcome") |>
  newSummarisedResult(settings = settings(data$incidence) |> mutate(group = "outcome")) |>
  visOmopResults::visOmopTable(
    estimateName = c(
      "Pregnancies" = "<denominator_count>",
      "Outcomes" = "<outcome_count> (<outcome_percentage> %)",
      "Outcomes in period" = "<outcome_in_period_count> (<outcome_in_period_percentage>%)",
      "Person-Days" = "<person_days_count>",
      "Person-Years" = "<person_years>",
      "Incidence" = c("<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)")
    ),
    header = c("estimate_name"),
    groupColumn = c("outcome"),
    hide = c("outcome_group", "gestational_trimester", "maternal_age_group", "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level"),
    columnOrder = c(
      "cdm_name", "outcome_group", "outcome", "gestational_trimester", "maternal_age_group", "pregnancy_start_period",  
      "socioeconomic_status", "ethnicity", "nationallity", "birth_continent", "variable_name", "variable_level", "estimate_name"
    ),
    factor = list(
      "cdm_name" = dbOrder,
      "gestational_trimester" = c("overall", "Trimester 1", "Trimester 2", "Trimester 3", "Postpartum"),
      "outcome_group" = c("Maternal Adverse Events", "AESI Sensitivity (180 wash-out)"),
      "outcome" = outcomeClean,
      "maternal_age_group" = c("overall", "12 to 17", "18 to 34", "35 to 55"),
      "pregnancy_start_period" = c("overall", "2018-2019", "2020-2021", "≥2021"),
      "socioeconomic_status" = c("overall", paste0("Q", 1:5)),
      "ethnicity" = c("overall", "White", "Black", "Asian", "Missing")
    ),
    rename = c("Database" = "cdm_name")
  ) |>
  set_table_properties(width = 1, layout = "autofit")
```

