---
title: "Background rates of maternal adverse events and adverse events of special interest during pregnancy: a cohort study of four European countries"
format:
  docx:
    reference-doc: ref.docx
    fig-cap-location: top
execute:
  echo: false
  message: false
  warning: false
---


```{r}
library(CohortCharacteristics)
library(dplyr)
library(ggplot2)
library(IncidencePrevalence)
library(markdown)
library(omopgenerics)
library(OmopSketch)
library(tidyr)
library(visOmopResults)
library(CohortSurvival)
library(flextable)
library(lme4)
library(broom)     
library(glmmTMB)
library(purrr)
library(patchwork)
library(ggh4x)

# whether to run meta analysis
runMetaAnalysis <- TRUE

# preprocess data if it has not been done
fileData <- file.path(getwd(), "data", "shinyData.RData")
if (!file.exists(fileData)) {
  source(file.path(getwd(), "data", "preprocess.R"))
}

# load shiny data
load(fileData)

# source functions
source(file.path(getwd(), "functions.R"))

# Quarto options
knitr::opts_chunk$set(
  out.width  = "95%",  # figures occupy ~95% of document width
  out.height = "auto",
  dpi        = 320,    # ensure figure quality
  fig.width  = 9,      # default aspect ratio (can be overridden per-figure)
  fig.height = 6,
  results    = "asis"  # enable Markdown produced via cat() inside chunks
)

maeCode <- c(
  "miscarriage", "ectopic_pregnancy", "stillbirth", 
  
  "gestational_diabetes", "preeclampsia", 
  "eclampsia", "hellp", "antepartum_haemorrhage",  
  
  "preterm_labour", "dysfunctional_labour", 
  
  "postpartum_haemorrhage", "postpartum_endometritis", 
  
  "maternal_death"
)
maeClean <- c(
  "Miscarriage", "Ectopic pregnancy", "Stillbirth",
  
  "Gestational diabetes", "Pre-eclampsia",
  "Eclampsia", "HELLP syndrome", "Antepartum haemorrhage", 
  
  "Preterm labour", "Dysfunctional labour",
  
  "Postpartum haemorrhage", "Postpartum endometritis", 
  
  "Maternal death"
)
aesiCode <- c(
  "pulmonary_embolism", "deep_vein_thrombosis", "tts",
  "immune_thrombocytopenia", "disseminated_intravascular_coagulation", 
  
  "myocarditis_or_pericarditis", "myocardial_infarction", 
  
  "ischaemic_stroke", "haemorrhagic_stroke",   
  
  "anaphylaxis", 
  
  "bells_palsy", "guillain_barre_syndrome", 
  "transverse_myelitis", "encephalitis", "narcolepsy"
)
aesiClean <- c(
  'Pulmonary embolism', 'Deep vein thrombosis', 'Thrombosis with thrombocytopenia syndrome', 
  'Immune thrombocytopenia', 'Disseminated intravascular coagulation', 
  
  'Myocarditis or pericarditis', 'Myocardial infarction', 
  
  'Ischaemic stroke', 'Haemorrhagic stroke', 
  
  'Anaphylaxis', 
  
  'Bell’s palsy', 'Guillain–Barré syndrome', 
  'Transverse myelitis', 'Encephalitis', 'Narcolepsy'
)
excludeCPRD <- c("Miscarriage", "Stillbirth")
dbOrder <- c("NLHR@UiO", "SCIFI-PEARL", "SIDIAP", "CPRD GOLD")

setGlobalTableOptions(type = "flextable")
```

:::{custom-style="Caption"}
Table 1. Characteristics of included pregnancies, stratified by database. 
:::

```{r}
# prepare results ----
data$summarise_characteristics |>
  dplyr::filter(group_level == "pregnancy_denominator", strata_name == "overall") |>
  dplyr::filter(
    !variable_name %in% c("Cohort start date", "Cohort end date", "Age", "Sex", "Prior observation", "Future observation")
  ) |>
  dplyr::mutate(
    estimate_value = if_else(variable_name == "Previous pregnancies", as.character(as.numeric(.data$estimate_value) - 1), .data$estimate_value),
    cdm_name = factor(cdm_name, levels = dbOrder),
    variable_level = dplyr::if_else(variable_name == "Previous pregnancies", "-", variable_level),
    variable_name = factor(
      variable_name,
      levels = c(
        "Number records", 
        "Maternal age", 
        "Maternal age group",
        "Days in cohort", 
        "Previous pregnancies", 
        "Covariates in the past 5 years",
        "History of comorbidities", 
        "Medications in the past year"
      ),
      labels = c(
        "Number pregnancies", 
        "Maternal age", 
        "Maternal age group",
        "Pregnancy length (days)", 
        "Previous pregnancies",
        "Covariates (previous 5 years)",
        "Comorbidities (any-time before)",
        "Medications (previous year)"
      )
    ),
    variable_level = factor(
      variable_level,
      levels = c(
        "12 to 17", "18 to 34", "35 to 55", "-", 
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse dependence", 
        
        "Asthma", "Diabetes", "Thyroid disorder", 
        "Essential hypertension", 
        "Systemic lupus erythematosus", "Hiv", 
        
        "Antidepressants", "Antiinflammatory antirheumatic", "Nsaids", 
        "Opioids", "Treatment acid related disorder", "Antiepileptics", 
        "Diabetes treatments"
      ),
      labels = c(
        "12 to 17", "18 to 34", "35 to 55", "-", 
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse dependence", 
        
        "Asthma", "Diabetes", "Thyroid disorder", 
        "Essential hypertension", 
        "SLE", "HIV", 
        
        "Antidepressants", "Antiinflammatory antirheumatic", "NSAIDs", 
        "Opioids", "Acid-related disorder treatments", "Antiepileptics", 
        "Diabetes treatments"
      )
    )
  ) |>
  dplyr::filter(!is.na(variable_name)) |>
  dplyr::arrange(cdm_name, variable_name, variable_level) |>
  visOmopTable(
    estimateName = c(
      "N (%)" = "<count> (<percentage>%)",
      "N" = "<count>",
      "Median [Q25 to Q75]" = "<median> [<q25> to <q75>]"
    ),
    rename = c("Database" = "cdm_name"),
    header = "cdm_name",
    hide = c("cohort_name", strataColumns(data$summarise_characteristics)),
    .options = list(keepNotFormatted = FALSE, groupAsColumn = TRUE),
    groupColumn = "variable_name"
  ) |>
  set_table_properties(width = 1, layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header") 
```


:::{custom-style="Caption"}
Table 2. Pooled Incidence Rates (per 100,000 person-years) and 95% Prediction Intervals for adverse events across four databases.

:::

```{r}
# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("overall", "gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Maternal Adverse Events", "Adverse Events of Special Interest")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count", "incidence_100000_pys", "incidence_100000_pys_95CI_lower", "incidence_100000_pys_95CI_upper", "outcome_in_period_count", "outcome_in_period_percentage"
  ))

# pool results ----
# --> model event counts using a Poisson distribution
# --> account for different amounts of person-time in each database
# --> random-effect for between-database heterogeneity. random intercept for database (1 | cdm_name)
# --> consider databases with zero events
if (runMetaAnalysis) {
  data$meta_incidence <- tidyIncidence |>
    filter(!is.na(outcome_count), !is.na(person_years)) |>
    group_by(
      outcome_cohort_name,
      gestational_trimester,
      maternal_age_group,
      pregnancy_start_period,
      outcome_group
    ) |>
    nest() |>
    mutate(
      meta = map(data, metaIR)
    ) |>
    unnest(meta) |>
    ungroup() |>
    select(!data)
  save(data, choices, selected, values, file = file.path(getwd(), "data", "shinyData.RData"))
} 

# display results ----
data$meta_incidence |>
  dplyr::filter(
    gestational_trimester == "overall",
    maternal_age_group == "overall",
    pregnancy_start_period == "overall"
  ) |>
  select(!c("gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  pivot_longer(
    cols = c("pooled_incidence_100000_pys", "predicted_interval_95CI_lower", "predicted_interval_95CI_upper", "tau2", "denominator_count", "outcome_count", "outcome_percentage", "number_of_databases", "person_years"),
    values_to = "estimate_value",
    names_to = "estimate_name"
  ) |>
  mutate(
    estimate_type = case_when(
      grepl("count", estimate_name) | estimate_name == "number_of_databases" ~ "integer",
      grepl("percentage", estimate_name) | estimate_name == "tau2" ~ "percentage",
      .default = "numeric"
    ),
    outcome = factor(.data$outcome_cohort_name, levels = c(aesiClean, maeClean)),
    estimate_value = as.character(estimate_value),
    outcome_group = factor(outcome_group, levels = c("Maternal Adverse Events", "Adverse Events of Special Interest"))
  ) |>
  filter(!is.na(outcome)) |>
  arrange(outcome_group, outcome) |>
  select(!"outcome_cohort_name") |>
  visTable(
    estimateName = c(
      "Databases (N)" = "<number_of_databases>",
      "Pregnancies (N)" = "<denominator_count>",
      "Outcomes (N (%))" = "<outcome_count> (<outcome_percentage>%)",
      "Person-Years" = "<person_years>",
      "IR (95% PI)" = "<pooled_incidence_100000_pys> (<predicted_interval_95CI_lower> to <predicted_interval_95CI_upper>)",
      "𝜏²" = "<tau2>"
    ),
    hide = "estimate_type",
    header = "estimate_name",
    groupColumn = "outcome_group",
    .options = list(decimals = c(integer = 0, percentage = 3, numeric = 2))
  ) |>
  set_table_properties(width = 1, layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header")
```

:::{custom-style="FooterNuria"}
Pooled incidence rates were estimated per 100,000 person-years using Poisson generalized linear mixed models with a random intercept for database; 95% prediction intervals reflect between-database heterogeneity. Source-specific estimates are shown in Supplementary Tables Sx. Databases with event counts <5 were clouded as per data-protection rules and were not included in pooled estimates. 
IR = Incidence Rate; PI = Prediction Interval; 𝜏² = estimated in between-database variance
:::
