---
title: "Background rates of Maternal Adverse Events and Adverse Events of Special Interest during pregnancy: a cohort study of four European countries"
format:
  docx:
    reference-doc: ref.docx
    fig-cap-location: top
execute:
  echo: false
  message: false
  warning: false
---


```{r}
library(CohortCharacteristics)
library(dplyr)
library(ggplot2)
library(IncidencePrevalence)
library(markdown)
library(omopgenerics)
library(OmopSketch)
library(tidyr)
library(visOmopResults)
library(CohortSurvival)
library(flextable)
library(lme4)
library(broom)     
library(glmmTMB)
library(purrr)
library(patchwork)
library(ggh4x)

# whether to run meta analysis
runMetaAnalysis <- FALSE

# preprocess data if it has not been done
fileData <- file.path(getwd(), "data", "shinyData.RData")
if (!file.exists(fileData)) {
  source(file.path(getwd(), "data", "preprocess.R"))
}

# load shiny data
load(fileData)

# source functions
source(file.path(getwd(), "functions.R"))

# Quarto options
knitr::opts_chunk$set(
  out.width  = "95%",  # figures occupy ~95% of document width
  out.height = "auto",
  dpi        = 360,    # ensure figure quality
  fig.width  = 9,      # default aspect ratio (can be overridden per-figure)
  fig.height = 6,
  results    = "asis"  # enable Markdown produced via cat() inside chunks
)

maeCode <- c(
  "miscarriage", "ectopic_pregnancy", "stillbirth", 
  
  "gestational_diabetes", "antepartum_haemorrhage", 
  "preeclampsia", "eclampsia", "hellp",  
  
  "preterm_labour", "dysfunctional_labour", 
  
  "maternal_death",
  
  "postpartum_haemorrhage", "postpartum_endometritis"
)
maeClean <- c(
  "Miscarriage", "Ectopic pregnancy", "Stillbirth",
  
  "Gestational diabetes mellitus", "Antepartum haemorrhage", 
  "Pre-eclampsia", "Eclampsia", "HELLP syndrome", 
  
  "Preterm delivery", "Dysfunctional labour",
  
  "Maternal death",
  
  "Postpartum haemorrhage", "Postpartum endometritis"
)
aesiCode <- c(
  "pulmonary_embolism", "deep_vein_thrombosis", 
  "immune_thrombocytopenia", "disseminated_intravascular_coagulation", "tts",
  
  "myocarditis_or_pericarditis", "myocardial_infarction", 
  
  "ischaemic_stroke", "haemorrhagic_stroke",   
  
  "bells_palsy", "guillain_barre_syndrome", 
  "transverse_myelitis", "encephalitis", "narcolepsy",
  
  "anaphylaxis"
)
aesiClean <- c(
  'Pulmonary embolism', 'Deep vein thrombosis',
  'Immune thrombocytopenia', 'Disseminated intravascular coagulation',
  'Thrombosis with thrombocytopenia syndrome', 
  
  'Myocarditis or pericarditis', 'Myocardial infarction', 
  
  'Ischaemic stroke', 'Haemorrhagic stroke', 
  
  'Bell’s palsy', 'Guillain–Barré syndrome', 
  'Transverse myelitis', 'Encephalitis', 'Narcolepsy',
  
  'Anaphylaxis'
)
excludeCPRD <- c("Miscarriage", "Dysfunctional labour")
excludeSCIFI <- c("Ectopic pregnancy")
dbOrder <- c("SCIFI-PEARL", "NLHR", "SIDIAP", "CPRD GOLD")

setGlobalTableOptions(type = "flextable")
```


:::{custom-style="Caption"}
Table 1. Outcome-specific patient follow-up. Time-at-rik that individuals contribute in the denominator for incidence rates estimation. 
:::

```{r}

dplyr::tibble(
  "Outcome" = c(
    "Adverse Events of Special Interest",
    "Ectopic pregnancies\nGestational diabetes mellitus\nPre-eclampsia\nEclampsia\nHELLP syndrome",
    "Miscarriage",
    "Stillbirth",
    "Antepartum haemorrhage",
    "Preterm delivery",
    "Dysfunctional labour",
    "Postpartum endometritis",
    "Postpartum haemorrhage",
    "Postpartum haemorrhage - sensitivity",
    "Maternal death"
  ),
  "Denominator" = c(
    "All pregnancies in the study population without occurrence of the AESI during the wash-out window.",
    "All pregnancies in the study population.",
    "All pregnancies in the study population.",
    "All pregnancies in the study population surviving up to gestational week 20.",
    "All pregnancies in the study population surviving up to gestational week 24.",
    "All pregnancies in the study population surviving up to gestational week 20.",
    "All pregnancies in the study population surviving up to gestational week 20.",
    "All pregnancies in the study poulation not ending in miscarriage.",
    "All pregnancies in the study poulation not ending in miscarriage.",
    "All pregnancies in the study poulation not ending in miscarriage.",
    "All pregnancies in the study poulation."
  ),
  "Follow-up" = c(
    "From pregnancy start until the earliest of: outcome occurrence, end of pregnancy, or end of available patient data.",
    "From pregnancy start until the earliest of: outcome occurrence, end of pregnancy, or end of available patient data.",
    "From pregnancy start until the earliest of: outcome occurrence, end of pregnancy, gestational week 19 + 6 days, or end of available patient data.",
    "From gestational week 20 until the earliest of: outcome occurrence, end of pregnancy, or end of available patient data.",
    "From gestational week 24 until the earliest of: outcome occurrence, end of pregnancy, or end of available patient data.",
    "From gestational week 20 until the earliest of: outcome occurrence, end of pregnancy, gestational week 37, or end of available patient data.",
    "From gestational week 20 until the earliest of: outcome occurrence, end of pregnancy, or end of available patient data.",
    "From pregnancy end date (included) until the earliest of: outcome occurrence, 6 weeks postpartum, next pregnancy, or end of available patient data.",
    "From pregnancy end date (included) until the earliest of: outcome occurrence, 12 weeks postpartum, next pregnancy, or end of available patient data.",
    "From pregnancy end date (not included) until the earliest of: outcome occurrence, 12 weeks postpartum, next pregnancy, or end of available patient data.",
    "From pregnancy start date until the earliest of: outcome occurrence, 6 weeks postpartum, or end of available patient data."
  )
) |>
  visTable() |>
  set_table_properties(layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header") |>
  flextable_to_rmd()
```

:::{custom-style="Caption"}
Table 2. Characteristics of all pregnancies included over the study period, stratified by data source.  
:::

```{r}
# prepare results ----
data$summarise_characteristics |>
  dplyr::filter(group_level == "pregnancy_denominator", strata_name == "overall") |>
  dplyr::mutate(
    cdm_name = factor(cdm_name, levels = dbOrder),
    variable_name = factor(
      variable_name,
      levels = c(
        "Number records", 
        "Number subjects",
        "Maternal age", 
        "Maternal age group",
        "Days in cohort", 
        "Pre-Pregnancy Smoke",
        "Covariates in the past year",
        "History of comorbidities", 
        "Medications in the past 6 months"
      ),
      labels = c(
        "Number\npregnancies, N", 
        "Number\nsubjects, N",
        "Maternal age,\nMedian [IQR]", 
        "Maternal age\ngroup, N(%)",
        "Pregnancy length\n(days), Median [IQR]", 
        "Smoking status,\nN(%)",
        "Comorbidities\n(prior year), N(%)",
        "Comorbidities\n(any-time before),\nN(%)",
        "Medications\n(prior 6 months),\nN(%)"
      )
    ),
    variable_level = factor(
      variable_level,
      levels = c(
        "12 to 17", "18 to 34", "35 to 55", "-",
        
        "No", "Yes", "No smoker", "Smoker", "Never smoker", "Former smoker", "Current some day smoker", "Missing",          
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse dependence",
        
        "Asthma", "Diabetes", "Thyroid disorder",
        "Essential hypertension",
        "Systemic lupus erythematosus", "Hiv",
        "Uterus malformations", "Polycystic ovary syndrome",
        "Chronic viral hepatitis", "Inflammatory bowel disease",
        
        "Antidepressants", "Antiinflammatory antirheumatic", "Nsaids",
        "Opioids", "Treatment acid related disorder", "Antiepileptics",
        "Diabetes treatments", "Antithrombotics", "Immunosupressants",
        "Corticosteroids"
      ),
      labels = c(
        "12 to 17", "18 to 34", "35 to 55", "-",
        
        "No", "Yes", "No", "Yes", "No", "Former smoker", "Yes", "Missing",   
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse\ndependence",
        
        "Asthma", "Diabetes", "Thyroid disorder",
        "Essential\nhypertension",
        "SLE", "HIV",
        "Uterus malformations", "PCOS",
        "Chronic viral\nhepatitis", "Inflammatory\nbowel disease",
        
        "Antidepressants", "Antiinflammatory/\nantirheumatic", "NSAIDs",
        "Opioids", "Acid-related disorder\ntreatments", "Antiepileptics",
        "Diabetes treatments", "Antithrombotics", "Immunosupressants",
        "Corticosteroids"
      )
    )
  ) |>
  dplyr::filter(!is.na(variable_name)) |>
  dplyr::arrange(cdm_name, variable_name, variable_level) |>
  visOmopTable(
    estimateName = c(
      "A" = "<count> (<percentage>%)",
      "b" = "<count>",
      "c" = "<median> [<q25> - <q75>]"
    ),
    rename = c("Data source" = "cdm_name"),
    header = "cdm_name",
    hide = c("cohort_name", strataColumns(data$summarise_characteristics), "estimate_name"),
    .options = list(keepNotFormatted = FALSE, groupAsColumn = TRUE, decimalMark = "·", bigMark = " "),
    groupColumn = "variable_name",
    factor = list(
      variable_name = c(
        "Number\npregnancies, N", 
        "Number\nsubjects, N",
        "Maternal age,\nMedian [IQR]", 
        "Maternal age\ngroup, N(%)",
        "Pregnancy length\n(days), Median [IQR]", 
        "Smoking status,\nN(%)",
        "Comorbidities\n(prior year), N(%)",
        "Comorbidities\n(any-time before),\nN(%)",
        "Medications\n(prior 6 months),\nN(%)"
      ),
      variable_level = c(
        "12 to 17", "18 to 34", "35 to 55", "-", NA,
        
        "No", "Yes", "Former smoker", "Missing",   
        
        "Obesity", "Depression", "Anxiety", "Alcohol misuse\ndependence",
        
        "Asthma", "Diabetes", "Thyroid disorder",
        "Essential\nhypertension",
        "SLE", "HIV",
        "Uterus malformations", "PCOS",
        "Chronic viral\nhepatitis", "Inflammatory\nbowel disease",
        
        "Antidepressants", "Antiinflammatory/\nantirheumatic", "NSAIDs",
        "Opioids", "Acid-related disorder\ntreatments", "Antiepileptics",
        "Diabetes treatments", "Antithrombotics", "Immunosupressants",
        "Corticosteroids"
      )
    )
  ) |>
  set_table_properties(layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header") 
```


:::{custom-style="FooterNuria"}
The study period went from January 2018 to March 2024 for SCIFI-PEARL, March 2023 for NLHR, and March 2025 for CPRD GOLD and SIDIAP.

NLHR = Norwegian Linked Health Registries; SCIFI-PEARL = Swedish Covid-19 Investigation for Future Insights – a Population Epidemiology Approach using Register Linkage; SIDIAP = Information System for Research in Primary Care Database; CPRD GOLD = Clinical Practice Research Datalink GOLD; SLE = Systemic Lupus Erythematosus; HIV= Human Immunodeficiency Virus; NSAIDs = Non-steroidal anti-inflammatory drugs
:::


:::{custom-style="Caption"}
Table 3. Incidence Rates (per 100,000 person-years) and 95% Confidence Intervals for Maternal Adverse Events across data sources, for the overall study period.
:::

```{r}
incTable <- data$incidence |>
  filterStrata(
    gestational_trimester == "overall",
    maternal_age_group == "overall",
    pregnancy_start_period == "overall",
    socioeconomic_status == "overall",
    ethnicity == "overall",
    birth_continent == "overall",
    nationallity == "overall"
  ) |>
  mutate(
    group_level = as.character(factor(.data$group_level, labels = c(maeClean, aesiClean), levels = c(maeCode, aesiCode))),
    estimate_value = if_else(
      estimate_name != "person_days_count", 
      estimate_value, 
      as.character(as.numeric(estimate_value)/365.25))
  ) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
   dplyr::filter(!(cdm_name == "SCIFI-PEARL" & group_level %in% excludeSCIFI)) |>
  filter(!is.na(group_level)) 

# add outcome percentage
incTable <- bind(
  incTable,
  incTable |>
    filter(estimate_name %in% c("denominator_count", "outcome_count")) |>
    pivotEstimates() |>
    mutate(
      estimate_value = as.character(outcome_count/denominator_count * 100),
      estimate_name = "outcome_percentage",
      estimate_type = "percentage"
    ) |>
    select(!c("denominator_count", "outcome_count")) |>
    newSummarisedResult(settings = settings(incTable))
)

# display MAE
incTable |>
  filterAdditional(outcome_group == "Maternal Adverse Events") |>
  mutate(
    additional_level = case_when(
      group_level %in% c("Miscarriage", "Ectopic pregnancy", "Stillbirth") ~ "Foetal Loss",
      group_level %in% c("Gestational diabetes mellitus", "Antepartum haemorrhage") ~ "Non-hypertensive Pregnancy Complications",
      group_level %in% c("Pre-eclampsia", "Eclampsia", "HELLP syndrome") ~ "Hypertensive Disorders of Pregnancy",
      group_level %in% c("Preterm delivery", "Dysfunctional labour") ~ "Perinatal Events",
      group_level %in% c("Postpartum haemorrhage", "Postpartum endometritis") ~ "Postpartum Events",
      .default = "Maternal Death"
    )
  ) |>
  visOmopTable(
    estimateName = c(
      "Pregnancies" = "<denominator_count>",
      "PYs" = "<person_years>",
      "Outcomes, N\n(Cumulative\nIncidence, %)" = "<outcome_count> (<outcome_percentage>%)",
      "IR per\n100,000 PYs\n(95% CI)" = "<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)"
    ),
    rename = c("Outcome" = "outcome_cohort_name", "Data source" = "cdm_name"), 
    header = "estimate_name",
    groupColumn = "outcome_group",
    factor = list(
      outcome_group = c("Foetal Loss", "Non-hypertensive Pregnancy Complications", "Hypertensive Disorders of Pregnancy", "Perinatal Events", "Postpartum Events", "Maternal Death"),
      outcome_cohort_name = c(maeClean, aesiClean),
      cdm_name = c(dbOrder)
    ),
    hide = c("gestational_trimester", "maternal_age_group", "pregnancy_start_period", "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_level", "variable_name"),
    columnOrder = c("outcome_group", "outcome_cohort_name", "cdm_name"),
    .options = list(decimals = c(integer = 0, percentage = 3, numeric = 2), keepNotFormatted = FALSE, delim = "8", decimalMark = "·", bigMark = " ")
  ) |>
  set_table_properties(layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header")
```
:::{custom-style="FooterNuria"}
The study period went from January 2018 to March 2024 for SCIFI-PEARL, March 2023 for NLHR, and March 2025 for CPRD GOLD and SIDIAP.

The number of pregnancies contributing to each outcome varied according to outcome-specific eligibility criteria.

Cumulative Incidence is given as number of outcomes per 100 pregnancies (%).

PY = Person-Years; IR = Incidence Rate; CI = Confidence Interval; NLHR = Norwegian Linked Health Registries; SCIFI-PEARL = Swedish Covid-19 Investigation for Future Insights – a Population Epidemiology Approach using Register Linkage; SIDIAP = Information System for Research in Primary Care Database; CPRD GOLD = Clinical Practice Research Datalink GOLD
:::



:::{custom-style="Caption"}
Table 4. Incidence Rates (per 100,000 person-years) and 95% Confidence Intervals for Adverse Events of Special Interes across data sources, for the overall study period.
:::

```{r}
# display MAE
incTable |>
  filterAdditional(outcome_group == "Adverse Events of Special Interest") |>
  mutate(
    additional_level = case_when(
      group_level %in% c("Pulmonary embolism", "Deep vein thrombosis") ~ "Venous Thromboembolic Events",
      group_level %in% c("Immune thrombocytopenia") ~ "Immune-mediated Haematologic Disorder",
      group_level %in% c("Thrombosis with thrombocytopenia syndrome", "Disseminated intravascular coagulation") ~ "Thrombotic and Coagulation Disorders",
      group_level %in% c("Myocarditis or pericarditis", "Myocardial infarction") ~ "Cardiovascular Events",
      group_level %in% c("Ischaemic stroke", "Haemorrhagic stroke") ~ "Cerebrovascular Events",
      group_level %in% c("Bell’s palsy", "Guillain–Barré syndrome", "Transverse myelitis", "Encephalitis", "Narcolepsy") ~ "Neurological (Immune-mediated) Events",
      .default = "Hypersensitivity"
    )
  ) |>
  visOmopTable(
    estimateName = c(
      "Pregnancies**" = "<denominator_count>",
      "PYs" = "<person_days_count>",
      "Outcomes, N\n(Cumulative\nIncidence, %)" = "<outcome_count> (<outcome_percentage>%)",
      "IR per\n100,000 PYs\n(95% CI)" = "<incidence_100000_pys> (<incidence_100000_pys_95CI_lower> - <incidence_100000_pys_95CI_upper>)"
    ),
    rename = c("Outcome" = "outcome_cohort_name", "Data source" = "cdm_name"), 
    header = "estimate_name",
    groupColumn = "outcome_group",
    factor = list(
      outcome_group = c("Venous Thromboembolic Events", "Immune-mediated Haematologic Disorder", "Thrombotic and Coagulation Disorders", "Cardiovascular Events", "Cerebrovascular Events", "Neurological (Immune-mediated) Events", "Hypersensitivity"),
      outcome_cohort_name = c(maeClean, aesiClean),
      cdm_name = c(dbOrder)
    ),
    hide = c("gestational_trimester", "maternal_age_group", "pregnancy_start_period", "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_level", "variable_name"),
    columnOrder = c("outcome_group", "outcome_cohort_name", "cdm_name"),
    .options = list(decimals = c(integer = 0, percentage = 3, numeric = 2), keepNotFormatted = FALSE, delim = "8", decimalMark = "·", bigMark = " ")
  ) |>
  set_table_properties(layout = "autofit") |>
  font(fontname = "calibri", part = "all") |>
  fontsize(size = 9, part = "body") |>
  fontsize(size = 10, part = "header")
```

:::{custom-style="FooterNuria"}
*Study Period: January 2018 to March 2024 [SCIFI-PEARL]; March 2023 [NLHR]; March 2025 [CPRD GOLD and SIDIAP]

** The number of pregnancies contributing to each outcome varied according to outcome-specific eligibility criteria

PY = Person-Years; IR = Incidence Rate; CI = Confidence Interval; NLHR = Norwegian Linked Health Registries; SCIFI-PEARL = Swedish Covid-19 Investigation for Future Insights – a Population Epidemiology Approach using Register Linkage; SIDIAP = Information System for Research in Primary Care Database; CPRD GOLD = Clinical Practice Research Datalink GOLD
:::

:::{custom-style="Caption"}
Figure 1. Incidence rates per 100,000 person-years for Maternal Adverse Events across data sources for the overall study period, stratified by gestational trimester.
:::

```{r, fig.height=6, fig.width=12}
# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Maternal Adverse Events")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
   dplyr::filter(!(cdm_name == "SCIFI-PEARL" & group_level %in% excludeSCIFI)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count"
  )) |>
  mutate(
    outcome_cohort_name = factor(.data$outcome_cohort_name, levels = maeClean),
    cdm_name = factor(cdm_name, dbOrder),
    gestational_trimester = factor(
      gestational_trimester, levels = c(paste0("Trimester ", 1:3), "Postpartum"), labels = c(paste0("Trimester\n", 1:3), "Post-\npartum")
    )
  ) |>
  arrange(cdm_name, outcome_cohort_name, gestational_trimester)

design_mat <- matrix(
  c(1:11, NA, 12:13, NA , NA),
  nrow = 4,
  byrow = TRUE
)

tidyIncidence |> 
  filter(maternal_age_group == "overall", pregnancy_start_period == "overall") |> 
  filter(!grepl("Postpartum", outcome_cohort_name)) |>
  pIncidence("gestational_trimester", "free", ribbon = FALSE, errorbar = TRUE) +
  facet_wrap(~ outcome_cohort_name, scales = "free")
```

:::{custom-style="FooterNuria"}
The study period went from January 2018 to March 2024 for SCIFI-PEARL, March 2023 for NLHR, and March 2025 for CPRD GOLD and SIDIAP.

Points represent the estimated incidence rate (per 100,000 person-years). Error bars indicate 95% Confidence Intervals (exact Poisson method); arrows denote intervals extending beyond the displayed axis limits.
:::


:::{custom-style="Caption"}
Figure 2. Incidence rates per 100,000 person-years for Maternal Adverse Events across data sources for the overall study period, stratified by maternal age
:::

```{r, fig.height=7, fig.width=11}
mae_age_limits_y <- c(
  "Eclampsia" = 150,
  "HELLP syndrome" = 300,
  "Maternal death" = 40,
  "Postpartum endometritis" = 8000,
  "Postpartum haemorrhage" = 20500
)

tidyIncidence |> 
   mutate(
    y_limit = case_when(
      outcome_cohort_name == "Eclampsia" ~ mae_age_limits_y["Eclampsia"],
      outcome_cohort_name == "HELLP syndrome" ~ mae_age_limits_y["HELLP syndrome"],
      outcome_cohort_name == "Maternal death" ~ mae_age_limits_y["Maternal death"],
      outcome_cohort_name == "Postpartum endometritis" ~ mae_age_limits_y["Postpartum endometritis"],
      outcome_cohort_name == "Postpartum haemorrhage" ~ mae_age_limits_y["Postpartum haemorrhage"],
      .default = NA
    ),
    arrow_end = ifelse(incidence_100000_pys_95CI_upper > y_limit, y_limit, NA)
  ) |>
  filter(maternal_age_group != "overall", pregnancy_start_period == "overall") |>
  pIncidence("maternal_age_group", "free_y", ribbon = FALSE, errorbar = TRUE) +
  ggh4x::facet_manual(~ outcome_cohort_name, design = design_mat, scales = "free_y")  +
  ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Eclampsia" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,mae_age_limits_y["Eclampsia"]), oob = scales::rescale_none),
       outcome_cohort_name == "HELLP syndrome" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,mae_age_limits_y["HELLP syndrome"]), oob = scales::rescale_none),
       outcome_cohort_name == "Maternal death" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,mae_age_limits_y["Maternal death"]), oob = scales::rescale_none),
       outcome_cohort_name == "Postpartum endometritis" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,mae_age_limits_y["Postpartum endometritis"]), oob = scales::rescale_none),
       outcome_cohort_name == "Postpartum haemorrhage" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(4000,mae_age_limits_y["Postpartum haemorrhage"]), oob = scales::rescale_none)
     )
   ) +
   geom_segment(
    aes(yend = arrow_end),
    arrow = arrow(length = unit(0.2, "cm")),
    linewidth = 0.6, alpha = 0.4,
    na.rm = TRUE
  )
```

:::{custom-style="FooterNuria"}
The study period went from January 2018 to March 2024 for SCIFI-PEARL, March 2023 for NLHR, and March 2025 for CPRD GOLD and SIDIAP.

Points represent the estimated incidence rate (per 100,000 person-years). Error bars indicate 95% Confidence Intervals (exact Poisson method); arrows denote intervals extending beyond the displayed axis limits.
:::

:::{custom-style="Caption"}
Figure 3. Incidence rates (per 100,000 person-years) for the four most frequent Adverse Events of Special Interest during pregnancy across data sources for the overall study period. Estimates are stratified by gestational trimester and maternal age.
:::

```{r, fig.height=6, fig.width=10}
aesi_trimester_limits_y <- c(
  "Deep vein thrombosis" = 360,
  "Pulmonary embolism" = 400,
  "Bell’s palsy" = 300,
  "Immune thrombocytopenia" = 350,
  "Anaphylaxis" = 150
)

aesi_age_limits_y <- c(
  "Deep vein thrombosis" = 350,
  "Pulmonary embolism" = 450,
  "Bell’s palsy" = 150,
  "Immune thrombocytopenia" = 175,
  "Anaphylaxis" = 150
)

# prepare results ----
tidyIncidence <- data$incidence |>
  dplyr::filter(strata_name %in% c("gestational_trimester", "maternal_age_group", "pregnancy_start_period")) |>
  omopgenerics::filterAdditional(outcome_group %in% c("Adverse Events of Special Interest")) |>
  dplyr::mutate(
    group_level = factor(
      .data$group_level, 
      levels = c(aesiCode, maeCode), 
      labels = c(aesiClean, maeClean)
    ),
    group_level = as.character(group_level)
  ) |>
  dplyr::filter(!is.na(group_level)) |>
  dplyr::filter(!(cdm_name == "CPRD GOLD" & group_level %in% excludeCPRD)) |>
   dplyr::filter(!(cdm_name == "SCIFI-PEARL" & group_level %in% excludeSCIFI)) |>
  tidy() |>
  select(!c(
    "socioeconomic_status", "ethnicity", "birth_continent", "nationallity", "variable_name", "variable_level", "person_days_count"
  )) |>
  filter(!outcome_cohort_name %in% c("Anaphylaxis", "Myocarditis or pericarditis", "Thrombosis with thrombocytopenia syndrome", "Narcolepsy", "Disseminated intravascular coagulation", "Encephalitis", "Guillain–Barré syndrome", "Myocardial infarction", "Transverse myelitis", "Ischaemic stroke", "Haemorrhagic stroke")) |>
  mutate(
    outcome_cohort_name = factor(.data$outcome_cohort_name, levels = aesiClean),
    cdm_name = factor(cdm_name, dbOrder),
    gestational_trimester = gsub(" ", "\n", gestational_trimester)
  ) |>
  arrange(cdm_name, outcome_cohort_name)

pTrimester <- tidyIncidence |> 
  mutate(
    y_limit = case_when(
      outcome_cohort_name == "Deep vein thrombosis" ~ aesi_trimester_limits_y["Deep vein thrombosis"],
      outcome_cohort_name == "Pulmonary embolism" ~ aesi_trimester_limits_y["Pulmonary embolism"],
      outcome_cohort_name == "Bell’s palsy" ~ aesi_trimester_limits_y["Bell’s palsy"],
      outcome_cohort_name == "Immune thrombocytopenia" ~ aesi_trimester_limits_y["Immune thrombocytopenia"],
      outcome_cohort_name == "Anaphylaxis" ~ aesi_trimester_limits_y["Anaphylaxis"],
      .default = NA
    ),
    arrow_end = ifelse(incidence_100000_pys_95CI_upper > y_limit, y_limit, NA)
  ) |>
  filter(maternal_age_group == "overall", pregnancy_start_period == "overall") |> 
  pIncidence("gestational_trimester", "free_y", ribbon = FALSE, errorbar = TRUE) +
   ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(10,aesi_trimester_limits_y["Deep vein thrombosis"]), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_trimester_limits_y["Pulmonary embolism"]), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_trimester_limits_y["Bell’s palsy"]), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_trimester_limits_y["Immune thrombocytopenia"]), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_trimester_limits_y["Anaphylaxis"]), oob = scales::rescale_none)
     )
   ) +
  ggtitle("A) Incidence Rates by Gestational Trimester") +
  theme(
    plot.title = element_text(hjust = -0.05, face = "bold", size = 15)
    # axis.text.x = element_text(angle = 60, vjust = 1, hjust = 1)
  ) +
  theme(legend.position = "none") +
  ylab("Incidence\n(per 100,000 person-years)") +
  geom_segment(
    aes(yend = arrow_end),
    arrow = arrow(length = unit(0.2, "cm")),
    linewidth = 0.6, alpha = 0.4,
    na.rm = TRUE
  )

pAge <- tidyIncidence |> 
  filter(gestational_trimester == "overall", pregnancy_start_period == "overall") |> 
    mutate(
    y_limit = case_when(
      outcome_cohort_name == "Deep vein thrombosis" ~ aesi_age_limits_y["Deep vein thrombosis"],
      outcome_cohort_name == "Pulmonary embolism" ~ aesi_age_limits_y["Pulmonary embolism"],
      outcome_cohort_name == "Bell’s palsy" ~ aesi_age_limits_y["Bell’s palsy"],
      outcome_cohort_name == "Immune thrombocytopenia" ~ aesi_age_limits_y["Immune thrombocytopenia"],
      outcome_cohort_name == "Anaphylaxis" ~ aesi_age_limits_y["Anaphylaxis"],
      .default = NA
    ),
    arrow_end = ifelse(incidence_100000_pys_95CI_upper > y_limit, y_limit, NA)
  ) |>
  pIncidence("maternal_age_group", "free_y", ribbon = FALSE, errorbar = TRUE) +
  theme(legend.position = "bottom") +
  # scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,150)) +
     ggh4x::facetted_pos_scales(
     y  = list(
       outcome_cohort_name == "Deep vein thrombosis" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_age_limits_y["Deep vein thrombosis"]), oob = scales::rescale_none),
       outcome_cohort_name == "Pulmonary embolism" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_age_limits_y["Pulmonary embolism"]), oob = scales::rescale_none),
       outcome_cohort_name == "Bell’s palsy" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_age_limits_y["Bell’s palsy"]), oob = scales::rescale_none),
       outcome_cohort_name == "Immune thrombocytopenia" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_age_limits_y["Immune thrombocytopenia"]), oob = scales::rescale_none),
       outcome_cohort_name == "Anaphylaxis" ~ scale_y_continuous(expand = expansion(mult = c(0.05, 0)), limits = c(0,aesi_age_limits_y["Anaphylaxis"]), oob = scales::rescale_none)
     )
   ) +
  ggtitle("B) Incidence Rates by Maternal Age") +
  theme(plot.title = element_text(hjust = -0.05, face = "bold", size = 15)) +
  ylab("Incidence\n(per 100,000 person-years)") +
  geom_segment(
    aes(yend = arrow_end),
    arrow = arrow(length = unit(0.2, "cm")),
    linewidth = 0.6, alpha = 0.4,
    na.rm = TRUE
  )

(pTrimester / pAge) + 
  plot_layout(heights = c(2, 1.93)) 
```

:::{custom-style="FooterNuria"}
The study period went from January 2018 to March 2024 for SCIFI-PEARL, March 2023 for NLHR, and March 2025 for CPRD GOLD and SIDIAP.

Points represent the estimated incidence rate (per 100,000 person-years). Error bars indicate 95% Confidence Intervals (exact Poisson method); arrows denote intervals extending beyond the displayed axis limits.
:::